---
output: 
    pdf_document: 
        latex_engine: xelatex
        template: template.tex
        keep_tex: true
documentclass: extarticle        
fontsize: 14pt
params:
  title: 
    label: Title for certificate
    value: "CERTIFICADO DE CONCLUSÃO"
    input: text
  attendee:
    label: Attendee
    value: Nome do participante
    input: text
  action_text: 
    label: Action text between name and workshop title.
    value: "participou do meetup"
    input: text
  workshop:
    label: Workshop title
    value: Nome do curso
    input: text
  date: 
    label: Date of workshop
    value: !r format(Sys.time(), "%d %B, %Y")
    input: date
  location:
    label: Location of workshop
    value: R-Ladies Natal
    input: text
  curriculum_title:
    lable: Header before curriculum content
    value: "Conteúdos do curso:"
    input: text
  curriculum:
    label: Path to file containing curriculum content
    value: !r system.file("rmarkdown", "templates", "workshop_certificate", "resources", "default_workshop_contents.md")
    input: file
  certifier:
    label: Certifying person full name
    value: Jeanne Raquel de Andrade Franco
  credentials:
    label: Certifying person credentials
    value: Organizadora 
    input: text
  organization:
    label: Decription of the organization running the workshops
    value: R-Ladies é uma organização mundial que tem a missão de promover a diversidade de gêneros na comunidade do R
    input: text
  organization_url:
    label: Organization URL without https://
    value: rladies.org/
    input: text
  signature:
    label: Path to file containing image of signature
    value: NULL
    input: file
  signature_skip:
    label: Space to skip between signature image and signature line, in cm.
    value: -0.4
    input: numeric
  border_image:
    label: Path to file containing border image
    value: !r system.file("rmarkdown", "extdata","assets")
    input: file
  papersize:
    label: Paper size of output PDF
    value: landscape
    input: text    
---

---
title: "`r params$title`"
classoption: "`r params$papersize`"
organization: "`r gsub("[\r\n]", " ", params$organization)`"
organization_url: "`r params$organization_url`"
border_image: "`r 'true'[params$border_image]`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE, 
                      fig.align = "center")
```

\begin{center}

\Large \textbf{
```{r attendee, results = 'asis'}
# thanks so much https://stackoverflow.com/questions/46226364/passing-parameters-in-rmarkdown-to-the-text-or-headings
cat(params$attendee)
```
}

\vspace{1.3cm}

\normalsize
```{r action_text, results = 'asis'}
cat(as.character(params$action_text), "\n")
```

\vspace{0.8cm}

\Large \textbf{
```{r workshop, results = 'asis'}
cat(as.character(params$workshop), "\n")
```
}
\normalsize

\large \textbf{
```{r location, results = 'asis'}
cat(as.character(params$date), " na comunidade ", params$location, "\n", sep = "")
```
}

\vspace{0.5cm}

\Large \textbf{
```{r curriculum_title, results = 'asis'}
cat(params$curriculum_title, "\n", sep = "")
```
}

\vspace{0.5cm}

\normalsize
\begin{varwidth}{0.8\textwidth}
```{r curriculum, results = 'asis'}
cat(params$curriculum, sep = "\n")
```

\end{varwidth}

\vfill


```{r signature, results = 'asis'}
if (!is.null(params$signature)){
  cat("\\includegraphics[height=2\\baselineskip]{signature} \\vspace{", 
      params$signature_skip, "cm}")
}
```

\rule[0in]{3in}{1pt}\\
\textbf{`r params$certifier`\\
        `r params$credentials`}\\
\vspace{0.8cm}

\end{center}
